---
title: "Simulation Results: Combined Figures"
output:
  pdf_document:
    latex_engine: xelatex
header-includes:
  - \usepackage{pdfpages}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r include-pdfs, results='asis'}
measures <- c("bias", "RMSE", "cor")
symmetry <- c("asym", "sym")
sigmas   <- c(7, 15)

pdf_files <- c()
for (measure in measures) {
for (s in symmetry) {
for (sig in sigmas) {
pdf_files <- c(pdf_files, paste0(measure, "_", s, "_", sig, ".pdf"))
}
}
}

# Emit LaTeX commands to include each PDF
cat(paste0("\\includepdf[pages=-]{", pdf_files, "}", collapse = "\n\n"))
```



% latex table generated in R 4.3.1 by xtable 1.8-4 package
% Fri Jan  9 11:10:24 2026
\begin{table}[ht]
\centering
\begin{tabular}{rrrr}
  \hline
 & BART & Probit & Sum \\ 
  \hline
Not significant & 32.00 & 46.00 & 78.00 \\ 
  Significant & 4.00 & 14.00 & 18.00 \\ 
  Sum & 36.00 & 60.00 & 96.00 \\ 
   \hline
\end{tabular}
\caption{Bias (mean-based)} 
\label{tab:ttest_bias}
\end{table}

% latex table generated in R 4.3.1 by xtable 1.8-4 package
% Fri Jan  9 11:10:24 2026
\begin{table}[ht]
\centering
\begin{tabular}{rrrr}
  \hline
 & BART & Probit & Sum \\ 
  \hline
Not significant & 12.00 & 14.00 & 26.00 \\ 
  Significant & 57.00 & 13.00 & 70.00 \\ 
  Sum & 69.00 & 27.00 & 96.00 \\ 
   \hline
\end{tabular}
\caption{RMSE} 
\label{tab:ttest_mse}
\end{table}

